%! Author = denis
%! Date = 09.06.2026

% Preamble
\documentclass[11pt]{article}

% Packages
\usepackage{amsmath}
\usepackage[margin=2.5cm]{geometry}
\usepackage{booktabs}
\usepackage{array}

\title{Cost and Time Estimation\\\large Sensor Data Collector (Mobile App)}
\author{Denis Schatzmann}
\date{\today}

% Document
\begin{document}

\maketitle

\section{Task}
The Sensor Data Collector lets a user pick sensors from a select box, add them
to a list (duplicates ignored), remove a marked sensor, and toggle data
collection with a Start/Stop button. On stop the collected data is sent to a
backend service. This report estimates size, effort, schedule and cost using
the methods from the lecture: Function Point Analysis for size and COCOMO for
effort and schedule.

\section{Size: Function Point Analysis}
Each function of the application is weighted with the low or average value from
the IFPUG categories.

\begin{table}[h]
\centering
\begin{tabular}{l l c}
\toprule
\textbf{Function} & \textbf{Category} & \textbf{FP} \\
\midrule
Add sensor                  & External input         & 3 \\
Remove marked sensor        & External input         & 3 \\
Start/Stop collection       & External input         & 3 \\
Send collected data to backend & External output     & 5 \\
Populate sensor select box  & External inquiry        & 4 \\
List of selected sensors    & Internal logical file   & 7 \\
\midrule
\textbf{Total} & & \textbf{25} \\
\bottomrule
\end{tabular}
\caption{Function point count.}
\end{table}

As a quick check, the widget point method counts four input widgets,
three describing widgets and one list, so $8 \times 2 = 16$ function points.
Both results place the application in the same small range, so the count of
about 25 FP is plausible.

\section{Effort: COCOMO}
The function points are converted to lines of code with the language table.
For a Java or Kotlin codebase the factor is 53 LOC per FP:
\[
\text{LOC} = 25 \times 53 = 1325 \approx 1.33 \text{ KDL}.
\]
Applying COCOMO in organic mode ($a = 3.2$, $b = 1.05$):
\[
E_i = 3.2 \cdot 1.33^{1.05} \approx 4.3 \text{ person months}.
\]
Because this is medical software, the required reliability cost factor is rated
high ($1.15$), giving an effort adjustment factor $EAF = 1.15$:
\[
E = EAF \cdot E_i = 1.15 \cdot 4.3 \approx 4.9 \text{ person months}.
\]

\section{Schedule and Staffing}
The duration and the average number of staff follow from the organic formulas:
\[
D = 2.5 \cdot E^{0.38} = 2.5 \cdot 4.9^{0.38} \approx 4.6 \text{ months},
\qquad
P = \frac{E}{D} \approx 1.1 \text{ persons}.
\]
So one developer working about $4.6$ months covers the work. With the effort
partitioning for a small project the $4.9$ person months split as:

\begin{table}[h]
\centering
\begin{tabular}{l c c}
\toprule
\textbf{Phase} & \textbf{Share} & \textbf{Person months} \\
\midrule
Design               & 19\% & 0.9 \\
Implementation       & 63\% & 3.1 \\
Integration and tests & 18\% & 0.9 \\
\bottomrule
\end{tabular}
\caption{Effort distribution for a small project.}
\end{table}

\section{Cost}
Total cost combines personnel, software and hardware. At a fully
loaded rate of about CHF 12'000 per person month, the personnel cost is
\[
4.9 \times 12'000 \approx \text{CHF } 59'000.
\]
Adding roughly CHF 4'000 for tooling licences, test devices and the cloud
backend gives a total of about \textbf{CHF 63'000} for one developer over about
\textbf{4.6 months}.

\section{Accuracy}
At the specification stage the estimate is only accurate within a factor of
about $0.5$ to $2$, so a range of roughly CHF 32'000 to CHF 126'000
should be communicated. The estimate assumes one cross platform codebase, an
existing backend API, and standard sensor access without custom drivers.

\end{document}
